\documentclass[11pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{ulem}
\normalem
\setlist[itemize]{leftmargin=*, itemsep=1pt, topsep=2pt}
\titleformat{\section}{\bfseries\large\underline}{}{0pt}{}
\pagenumbering{gobble}

\begin{document}

\begin{center}
    {\LARGE \textbf{Dhanunjaya Andavarapu}}\\
    \vspace{4pt}
    Backend Developer\\
    \vspace{4pt}
    \href{mailto:dhanunjaya.andavarapu@outlook.com}{dhanunjaya.andavarapu@outlook.com} \quad | \quad
    \href{tel:+919177299229}{+91 91772 99229} \quad | \quad
    Hyderabad, Telangana\\
    \vspace{4pt}
    \href{https://github.com/Dhanunjaya235}{github.com/Dhanunjaya235} \quad | \quad
    \href{https://www.linkedin.com/in/dhanunjaya-andhavarapu-502492246}{linkedin.com/in/dhanunjaya-andhavarapu-502492246} \quad | \quad
    \href{https://www.blogger.com/blog/pages/2357939272283650645}{blogger} \quad | \quad
    \href{https://www.npmjs.com/settings/dhanunjay/packages}{npm profile}
\end{center}

%----------------------- SUMMARY -----------------------%
\section*{Professional Summary}
Backend Software Engineer with 3+ years of experience building scalable APIs, distributed services, and data-intensive systems using Python, FastAPI, Django, Java Spring Boot, and PostgreSQL. Strong expertise in system design, performance tuning, SQL optimization, authentication/authorization, observability, CI/CD, and cloud-native deployments. Experienced in delivering secure, reliable backend services with clean API contracts and modular architectures.

%----------------------- SKILLS -----------------------%
\section*{Core Skills}
\textbf{Languages:} Python, Java, TypeScript \\
\textbf{Backend:} FastAPI, Django/DRF, Flask, Spring Boot, Express.js \\
\textbf{Databases:} PostgreSQL, MongoDB, Redis \\
\textbf{Cloud/CI/CD:} AWS, Git, GitHub Actions, Azure DevOps \\
\textbf{DevOps/Tools:} Docker, Terraform, NGINX, Postman, OpenAPI/Swagger \\
\textbf{Backend Expertise:} REST APIs, RBAC, JWT Auth, Caching, SQL tuning, Observability, Background workers, Webhooks, Postman

%----------------------- EXPERIENCE -----------------------%
\section*{Experience}

\textbf{Backend Software Engineer} \hfill \textbf{Cognine Technologies} \\
Hyderabad, India \hfill 2023 -- Present
\begin{itemize}
    \item Developed scalable REST APIs using FastAPI, Django, and Spring Boot with clean architecture and modular services.
    \item Improved P95 latency by 35\% through SQL query optimization, composite indexing, and Redis caching.
    \item Implemented RBAC, JWT auth, secure configuration management, and secret rotation policies.
    \item Automated CI/CD pipelines using GitHub Actions/Azure; integrated migration gates and rollout strategies.
    \item Championed API versioning, error handling standards, and contract testing for reliable integrations.
\end{itemize}

\textbf{Associate Software Engineer} \hfill \textbf{Cognine Technologies} \\
Hyderabad, India \hfill 2022 -- 2023
\begin{itemize}
    \item Built backend services with Flask, Django, and FastAPI including models, migrations, and validated endpoints.
    \item Added rate limiting, validation layers (Pydantic/DRF), and pagination to improve API reliability.
    \item Implemented scheduled workers for reporting, emails, and cleanup jobs using Celery/RQ.
    \item Wrote API docs (OpenAPI/Swagger) and onboarding documentation to streamline collaboration.
\end{itemize}

%----------------------- PROJECTS -----------------------%
\section*{Projects}

\textbf{Payment Orchestrator Service} \hfill Backend Service \\
FastAPI, PostgreSQL, Redis, Celery, Stripe, Docker
\begin{itemize}
    \item Designed PCI-conscious orchestration handling multiple payment providers with idempotency, retries, and DLQs.
\end{itemize}

\textbf{Project Tracker (Backend)} \hfill Spring Boot System \\
Spring Boot, MyBatis, PostgreSQL
\begin{itemize}
    \item Built project/sprint tracking backend with RBAC, audit logs, CTEs, composite indexes, and optimized queries.
\end{itemize}

\textbf{ESPO – Sports Platform Backend} \hfill API + Auth \\
Spring Boot, JPA, JWT
\begin{itemize}
    \item Developed RBAC-secured APIs, leaderboard services, and configurable admin workflows.
\end{itemize}

\textbf{Benefits Portal (Backend)} \hfill Flask API \\
Flask, SQLAlchemy, Alembic, S3
\begin{itemize}
    \item Built secure REST APIs, file storage adapters, report generation jobs, and robust error-handling middleware.
\end{itemize}

\textbf{SAT Platform Backend \& API Services} \hfill DRF System \\
Django, DRF, PostgreSQL, Docker
\begin{itemize}
    \item Delivered assessment, analytics, and feedback APIs with dynamic filtering and modular architecture.
\end{itemize}

\textbf{StaffX Backend API} \hfill Production API \\
FastAPI, SQLAlchemy, Alembic, JWT
\begin{itemize}
    \item Implemented modular routing, versioned endpoints, strict Pydantic validation, and secure JWT auth flows.
\end{itemize}

%----------------------- POCs -----------------------%
\section*{Proof of Concepts (POCs)}
\textbf{SmartMail – AI Email Automation (Backend)} \hfill FastAPI + RAG \\
\begin{itemize}
    \item Built RAG-powered backend with classification, vector DB, background workers, webhook ingestion, and retries.
\end{itemize}
\textbf{Athena Health Integration Service} \hfill Flask + OAuth \\
\begin{itemize}
    \item Developed OAuth-secured integrations, rate-limit aware sync jobs, and conflict resolution pipelines.
\end{itemize}
\textbf{Healthcare Data Aggregation API} \hfill Django + DRF \\
\begin{itemize}
    \item Aggregated multi-provider EHR data, normalized schemas, and exposed FHIR-like read models.
\end{itemize}
\textbf{Train Schedule API} \hfill Express + MongoDB \\
\begin{itemize}
    \item Implemented schedule search, JWT auth, caching, pagination, and seeded testing environment.
\end{itemize}

%----------------------- ACHIEVEMENTS -----------------------%
\section*{Achievements}
\textbf{Star of the Quarter (2024)} • \textbf{Team Player Award (2023)} • \textbf{Hackathon Winner – 1st Place (2025)}

%----------------------- EDUCATION -----------------------%
\section*{Education}
\textbf{B.Tech in Computer Science and Engineering} \hfill 2018 -- 2022 \\
Rajiv Gandhi University of Knowledge and Technologies (IIIT)
\end{document}