\documentclass[11pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{ulem}
\normalem
\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=2pt}
\titleformat{\section}{\bfseries\large\underline}{}{0pt}{}
\pagenumbering{gobble}

\begin{document}

\begin{center}
    {\LARGE \textbf{Dhanunjaya Andavarapu}}\\
    \vspace{4pt}
    Frontend Developer\\
    \vspace{4pt}
    \href{mailto:dhanunjaya.andavarapu@outlook.com}{dhanunjaya.andavarapu@outlook.com} \quad | \quad
    \href{tel:+919177299229}{+91 91772 99229} \quad | \quad
    Hyderabad, Telangana\\
    \vspace{4pt}
    \href{https://github.com/Dhanunjaya235}{github.com/Dhanunjaya235} \quad | \quad
    \href{https://www.linkedin.com/in/dhanunjaya-andhavarapu-502492246}{linkedin.com/in/dhanunjaya-andhavarapu-502492246} \quad | \quad
    \href{https://www.blogger.com/blog/pages/2357939272283650645}{blogger} \quad | \quad
    \href{https://www.npmjs.com/settings/dhanunjay/packages}{npm profile}
\end{center}

%----------------------- SUMMARY -----------------------%
\section*{Professional Summary}
Frontend-focused Full Stack Developer with 3+ years of experience building scalable, high-performance web applications using React, TypeScript, Redux, Tailwind, and modern frontend ecosystems. Strong expertise in component architectures, design systems, animations, UI/UX implementation, and frontend performance optimization. Experienced in integrating APIs, building secure and reusable frontends, collaborating with designers, and delivering enterprise-grade user experiences.

%----------------------- SKILLS -----------------------%
\section*{Core Skills}
\textbf{Frontend:} React, Next.js, Redux Toolkit, Context API, Tailwind CSS, Material UI, SCSS, Styled Components, Framer Motion \\
\textbf{Languages:} TypeScript, JavaScript, HTML5, CSS3 \\
\textbf{Testing:} Jest, React Testing Library, Storybook \\
\textbf{Design:} Figma, Axure RP, UI Prototyping, Responsive Design \\
\textbf{Tools:}  Vite, Webpack, GitHub Actions, Vercel, AWS Amplify \\
\textbf{Backend (supporting):} FastAPI, Flask, Node.js, PostgreSQL \\
\textbf{Cloud/DevOps:} AWS, Docker, Terraform, Jenkins, GitHub Actions, Azure DevOps \\
\textbf{Version Control:} Git, Github, Azure Repos \\
\textbf{Development Tools:} Postman, Visual Studio Code

%----------------------- EXPERIENCE -----------------------%
\section*{Experience}

\textbf{Frontend Developer} \hfill \textbf{Cognine Technologies} \\
Hyderabad, India \hfill 2023 -- Present
\begin{itemize}
    \item Developed and maintained scalable React applications with TypeScript, Redux Toolkit, Tailwind CSS, and Material UI.
    \item Built reusable design-system components and contributed to frontend architecture initiatives across multiple teams.
    \item Delivered intuitive dashboards, admin tools, data visualizations, and high-performance user interfaces.
    \item Implemented advanced animations and transitions using \textbf{Framer Motion} for rich interactive user experiences.
    \item Collaborated with UX designers to ensure pixel-perfect designs and consistent UI patterns.
    \item Optimized frontend performance, accessibility, and cross-browser compatibility.
    \item Awarded \textbf{Star of the Quarter} and secured \textbf{1st place} in an internal hackathon for building an AI-powered UI solution.
\end{itemize}

\textbf{Associate Frontend Developer} \hfill \textbf{Cognine Technologies} \\
Hyderabad, India \hfill 2022 -- 2023
\begin{itemize}
    \item Developed responsive UI components using React, Material UI, and SCSS for enterprise applications.
    \item Improved UX by fixing layout issues, optimizing performance, and refining navigation workflows.
    \item Collaborated with designers and senior developers to clarify UI/UX requirements and deliver high-quality screens.
    \item Awarded the \textbf{Team Player Award} for collaboration and support in frontend initiatives.
\end{itemize}

%----------------------- PROJECTS -----------------------%
\section*{Projects}

\textbf{Common Components With React} \hfill Component Library \\
React, TypeScript, Context API, Jest, MUI, Jenkins
\begin{itemize}
    \item Developed a reusable component library used by 13+ teams to standardize UI and accelerate development.
\end{itemize}

\textbf{ESPO – Organizational Sports Platform} \hfill Frontend App \\
React, Context API, Tailwind, Framer Motion
\begin{itemize}
    \item Built animated leaderboards, dynamic tournament screens, and responsive UI using Framer Motion.
\end{itemize}

\textbf{AI-Powered SAT Prep Platform} \hfill Web App \\
React, Redux Toolkit, Tailwind, Stripe, Amplify
\begin{itemize}
    \item Built student dashboards, analytics, and payment flows; integrated AWS Amplify + Cognito authentication.
\end{itemize}

\textbf{StaffX – Staffing Management Platform} \hfill Full-Stack Application \\
React, TypeScript, Redux Toolkit, Tailwind, FastAPI, PostgreSQL
\begin{itemize}
    \item Developed a full-stack enterprise staffing platform with RBAC, advanced filtering, and document previews.
\end{itemize}

\textbf{Benefits Portal (Frontend)} \hfill Frontend Platform \\
React, Context API, Material UI
\begin{itemize}
    \item Built reusable UI modules, responsive forms, and interactive dashboards for employee benefits management.
\end{itemize}

%----------------------- POCs -----------------------%
\section*{Proof of Concepts (POCs)}

\textbf{SmartMail – AI Email Automation UI} \hfill React + Tailwind \\
\begin{itemize}
    \item Built an interactive AI automation dashboard with real-time email processing visualization and animations.
\end{itemize}

\textbf{Athena Health Integration UI Demo} \hfill React + MUI \\
\begin{itemize}
    \item Developed a demo UI showcasing real-time healthcare API integration with smooth workflows and loaders.
\end{itemize}

\textbf{Healthcare UI/UX Prototype} \hfill Axure RP \\
\begin{itemize}
    \item Designed interactive prototypes covering onboarding, scheduling, and patient workflows.
\end{itemize}

\textbf{Train Schedule App Frontend} \hfill React Native \\
\begin{itemize}
    \item Built mobile UI with intuitive navigation, animations, and real-time schedule views.
\end{itemize}

%----------------------- ACHIEVEMENTS -----------------------%
\section*{Achievements}
\textbf{Star of the Quarter (2024)} • \textbf{Team Player Award (2023)} • \textbf{Hackathon Winner – 1st Place (2025)}

%----------------------- EDUCATION -----------------------%
\section*{Education}
\textbf{B.Tech in Computer Science and Engineering} \hfill 2018 -- 2022 \\
Rajiv Gandhi University of Knowledge and Technologies (IIIT)
\end{document}