\documentclass[11pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{ulem}
\normalem
\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=2pt}
\titleformat{\section}{\bfseries\large\underline}{}{0pt}{}
\pagenumbering{gobble}

\begin{document}

\begin{center}
    {\LARGE \textbf{Dhanunjaya Andavarapu}}\\
    \vspace{4pt}
    Full Stack Developer\\
    \vspace{4pt}
    \href{mailto:dhanunjaya.andavarapu@outlook.com}{dhanunjaya.andavarapu@outlook.com} \quad | \quad
    \href{tel:+919177299229}{+91 91772 99229} \quad | \quad
    Hyderabad, Telangana\\
    \vspace{4pt}
    \href{https://github.com/Dhanunjaya235}{github.com/Dhanunjaya235} \quad | \quad
    \href{https://www.linkedin.com/in/dhanunjaya-andhavarapu-502492246}{linkedin.com/in/dhanunjaya-andhavarapu-502492246} \quad | \quad
    \href{https://www.blogger.com/blog/pages/2357939272283650645}{blogger} \quad | \quad
    \href{https://www.npmjs.com/settings/dhanunjay/packages}{npm profile}
\end{center}

\section*{Professional Summary}
Dynamic and results-driven Full Stack Developer with 3+ years hands-on experience in designing, building, and deploying robust web applications. Skilled in both front-end and back-end development leveraging modern frameworks, clean architecture, and best practices to deliver high-performance, scalable solutions. Demonstrates strong ability to collaborate with cross-functional teams, translate business requirements into technical designs, and deliver production-ready code on schedule. Proficient in working across the full software development lifecycle including UI/UX, API design, database modeling, testing, and deployment. Committed to writing clean, maintainable code and continuously learning new technologies to solve real-world problems.

%----------------------- SKILLS -----------------------%
\section*{Core Skills}
\textbf{Languages:} TypeScript, JavaScript, Python, Java \\
\textbf{Frontend:} React, Redux, Angular, Tailwind, MUI, Framer Motion \\
\textbf{Backend:} Django, DRF, FastAPI, Flask, Spring Boot, Express.js, MyBatis \\
\textbf{Testing:} Jest, React Testing Library \\
\textbf{Cloud/DevOps:} AWS, Docker, Terraform, Jenkins, GitHub Actions, Azure DevOps \\
\textbf{Databases:} PostgreSQL, MongoDB, SQL (CTEs, joins, aggregations) \\
\textbf{Version Control:} Git, Github, Azure Repos \\
\textbf{Practices:} REST APIs, Clean Architecture, CI/CD, Agile \\
\textbf{Development Tools:} Postman, Visual Studio Code

%----------------------- EXPERIENCE -----------------------%
\section*{Experience}

\textbf{Software Engineer} \hfill \textbf{Cognine Technologies} \\
Hyderabad, India \hfill 2023 -- Present
\begin{itemize}
    \item Built a reusable \textbf{React component library} used by 13+ teams; automated CI/CD with Jenkins.
    \item Delivered full-stack features across React, Django, FastAPI, Spring Boot, PostgreSQL.
    \item Led an \textbf{AI-driven hackathon project} that won 1st place; improved performance and UX.
    \item Standardized UI design patterns and reusable components across projects.
    \item Developed POCs with LangChain, AWS Amplify, and Electron.
\end{itemize}

\textbf{Associate Software Engineer} \hfill \textbf{Cognine Technologies} \\
Hyderabad, India \hfill 2022 -- 2023
\begin{itemize}
    \item Delivered backend APIs and frontend modules using Flask, Django, and React.
    \item Authored onboarding documentation and improved development workflows.
    \item Built reusable data models and API integrations; recognized with \textbf{Team Player Award}.
\end{itemize}

%----------------------- PROJECTS -----------------------%
\section*{Projects}
\textbf{AI-Powered SAT Prep Platform} \hfill Web App \\
React, Redux Toolkit, Amplify, Stripe
\begin{itemize}
    \item Built dashboards, analytics, payments, and authentication using AWS Amplify + Cognito.
\end{itemize}

\textbf{SAT Backend Services} \hfill API System \\
Django, DRF, PostgreSQL, Docker
\begin{itemize}
    \item Developed scalable APIs for assessments, analytics, and role management.
\end{itemize}

\textbf{Common Components With React} \hfill Frontend System \\
React, Context API, Jest, MUI, Jenkins
\begin{itemize}
    \item Built a scalable component library for 13+ teams; improved UI consistency and developer velocity.
\end{itemize}

\textbf{Staffing Management} \hfill Full-Stack Application \\
Python, Fast API, PostgreSQL, SQLAlchemy
\begin{itemize}
    \item Built a full-stack staffing and recruitment platform with role-based access, advanced client/vendor/job/candidate modules, and scalable FastAPI–PostgreSQL backend integrated with a React + TypeScript frontend.
\end{itemize}
\textbf{Project Tracker} \hfill Backend Application \\
Java, Spring Boot, MyBatis, PostgreSQL
\begin{itemize}
    \item Designed backend services for project/sprint tracking with optimized SQL and secure APIs.
\end{itemize}

\textbf{ESPO – Organizational Sports Platform} \hfill Full-Stack App \\
React, Spring Boot, JPA
\begin{itemize}
    \item Developed animated leaderboards, role-based dashboards, and interactive tournament workflows.
\end{itemize}

\textbf{Benefits Portal} \hfill Full-Stack Platform \\
React, Flask, SQLAlchemy
\begin{itemize}
    \item Built secure APIs, Excel reporting, and reusable UI modules for employee benefits management.
\end{itemize}

%----------------------- POCs (COMPRESSED) -----------------------%
\section*{POCs}

\textbf{SmartMail – AI Email Automation} \hfill FastAPI + React  
\begin{itemize}
    \item Built RAG-based email automation prototype using FastAPI, LangChain, and Groq LLMs.
\end{itemize}

\textbf{Athena Health Integration Demo} \hfill React + Flask  
\begin{itemize}
    \item Developed UI workflows and sync mechanisms showcasing real-time Athena API integration.
\end{itemize}

\textbf{Healthcare UI/UX Prototype} \hfill Axure RP  
\begin{itemize}
    \item Designed interactive flows including onboarding, scheduling, and health record access.
\end{itemize}

\textbf{Train Schedule App (Clone)} \hfill Express + React Native  
\begin{itemize}
    \item Built learning POC replicating core train-tracking features using JWT-secured APIs.
\end{itemize}

%----------------------- ACHIEVEMENTS -----------------------%
\section*{Achievements}
\textbf{Team Player Award (2023)}, \textbf{Star of the Quarter (2024)}, \textbf{Hackathon Winner – 1st Place (2025)}

%----------------------- EDUCATION -----------------------%
\section*{Education}
\textbf{B.Tech in Computer Science and Engineering} \hfill 2018 -- 2022 \\
Rajiv Gandhi University of Knowledge and Technologies (IIIT)

\end{document}